Fig 2

### 2020-08-24 analysis/figure-2.Rmd
working on upsets

png("../figures/fig4-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig4) 
dev.off()

sessionInfo()
```

>>>>

png("../figures/fig4-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig4) 
dev.off()
```

```{r refs}
sessionInfo()
```

```{r}
head(allDEG)

library(UpSetR)
head(allDEG)

MG <- allDEG %>%
  filter(sex == "male", tissue == "hypothalamus", 
         comparison %in% comparisonlevelsreplace) %>%
  select(sex, tissue, comparison, gene) %>%
  mutate(seen = 1) %>%
  pivot_wider(names_from = comparison, values_from = seen)
MG

upset(MG) 
```
